Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-27 paper/paper.tex
Added more refs to paper and bibtex file.

\cite{BockAlexander2018TITE}
\cite{KonovalovD2017RDfA}
\cite{Williams:2020:UIF}

>>>>

Bock 2018 \cite{BockAlexander2018TITE},
Konovalov 2017 \cite{KonovalovD2017RDfA},
Williams 2020 \cite{Williams:2020:UIF},
Hao 2015 \cite{Hao2015TheMO},
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Wang 2015 \cite{Huihui2015StudyOT},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Bernardo 2020 \cite{Bernardo2020FishQI},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Dowlati 2012 \cite{Dowlati2012ApplicationOM},
Balaban 2010 \cite{Balaban2010UsingIA},
Alsmadi 2010 \cite{Alsmadi2010FishRB},
Isimen 2014 \cite{Iscimen2014ImageAM},
Iqbal 2021 \cite{Iqbal2021AutomaticFS},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020DeepLA}
